RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-31 casestudies.tex
the easy vis language for analyst

Finally, consider the situation where an analyst wants to understand
the price dynamics of stocks with respects to various attributes and
time ranges. For this, interactive visualization may be very helpful.
In our example, the analyst creates an interactive tool with N views.
\todo{Describe dcplot and notebook which uses it.}

>>>>

Finally, consider the situation where an analyst wants to understand
the price dynamics of stocks with respects to various attributes and
time ranges. For this, interactive visualization may be very helpful.
In our example, the analyst creates an interactive tool with N views.

Through the tight integration of R and JavaScript functions and data,
the analyst writes a function in R which passes the dataframe and the
description of the charts to the dcplot library.  Simple R expressions
are captured as trees to generate JavaScript expressions.  The terse
chart description language, with intelligent defaults inspired by
ggplot2, provides a simple yet powerful interface to the grouping
and reduction functionality of crossfilter and the chart styles of
dc.js and d3.js.
